### 2021-06-29 about/vita.tex
Lattice of arithmetic progressions
Indepno

\pubbegin S
\subitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. {\sl arXiv preprint 2007.05681}.
Submitted July 2020.
\subitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set. {\sl arXiv preprint 2012.12339}.
Submitted December 2020.
\subitem (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl arXiv preprint 2105.12046}.
Submitted May 2021.

\goodbreak

@@

\leftright{\bf Probabilistic analysis of branching processes}{\bf May 2020 -- present}
\leftright{\sl Research group}{\sl McGill University}
\smallskip
Ongoing research on branching processes, headed by Luc Devroye. Studied estimation problems
on Galton-Watson trees. Attended informal seminars over the year, discussing
various topics related to branching
processes. (Gave a presentation at five of these: one on root estimation in Galton-Watson
trees, two on generating functions and elementary analytic combinatorics, and two on graph regularity.)
[S1, S3]

>>>>

\pubbegin S
\subitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. {\sl arXiv preprint 2007.05681}, 20~pp.
Submitted July 2020.
\subitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set. {\sl arXiv preprint 2012.12339}, 11~pp.
Submitted December 2020.
\subitem (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl arXiv preprint 2105.12046}, 11~pp.
Submitted May 2021.
\subitem (with Jad Hamdan) The lattice of arithmetic progressions. {\sl arXiv preprint 2106.05949}, 8~pp.
Submitted June 2021.
\subitem (with Luc Devroye and Rosie Y. Zhao) The independence number of a Bienaym\'e--Galton--Watson tree
and related parameters. {\sl arXiv preprint 2106.14389}, 20~pp.
Submitted June 2021.

@@

\leftright{\bf Probabilistic analysis of branching processes}{\bf May 2020 -- present}
\leftright{\sl Research group}{\sl McGill University}
\smallskip
Ongoing research on branching processes, headed by Luc Devroye. Studied estimation problems
on Galton-Watson trees. Attended informal seminars over the year, discussing
various topics related to branching
processes. (Gave a presentation at five of these: one on root estimation in Galton-Watson
trees, two on generating functions and elementary analytic combinatorics, and two on graph regularity.)
[S1, S3, S5]
